---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
```

# monsteR

A list of D&D 5e monsters provided through SRD and some functions to fiddle with them.

Data is taken from the json file shared by [u/droiddruid](https://www.reddit.com/r/dndnext/comments/43a09o/srd_monsters_in_json_format/) combined with the human readable files from [open5e](https://github.com/eepMoody/open5e).

## Installation

```r
devtools::install_github('oganm/monsteR')
```

## Usage

The package includes a list that include all SRD monsters called `monsters`. Each element of this list is a list that holds monster attributes

```{r}
ls(monsters$Acolyte)

monsters$Acolyte$actions
```

Individual monsters have a special print function (`print.monster`). When a monster is called, the text taken from open5e is displayed

```{r}
monsters$Acolyte
```

The package includes an `attack` function. This function looks at all available actions of a monster, detects if they have attack rolls and damage dice associated with them, and rolls the dice

```{r}
attack(monsters$`Bandit Captain`)
```

If the monster is a spellcaster it will have a `spellcasting` list which lists spell DC, spell attack bonus and spells. Note that spells are `spellList` objects from [wizaRd](https://github.com/oganm/wizaRd) package.

```{r}
monsters$Acolyte$spellcasting

monsters$Acolyte$spellcasting$spells$`Cure Wounds`
```
